---
title: "My Shiny App"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My Shiny App

The mtcars dataset is a great way to practice linear regression skills. 

My Shiny App has been created to help you on visualizing the outcome of your model according to variable selection.

## Shiny App functionality

Select independent variable and submit. The server calculations fit a linear model and return the resulting plot.

```{r,eval=FALSE,echo=TRUE}
server=function(input, output) {
  model<- reactive({
    varInput<-input$variable
    colnum<-match(varInput,names(mtcars))
    df<-data.frame(mpg=mtcars$mpg,mtcars[,colnum])
    colnames(df)[2]<-varInput
    fit<-lm(mpg~.,data=df)
  })   
  output$plot1<-renderPlot({
    varInput<-input$variable
    colnum<-match(varInput,names(mtcars))
    df<-data.frame(mpg=mtcars$mpg,mtcars[,colnum])
    colnames(df)[2]<-varInput
    plot(df[,2],df$mpg,xlab=colnames(df)[2],ylab="mpg")
    abline(model(),col="red",lwd=2)
  })})
```

## Interactive Plot 
```{r echo=FALSE}
shinyApp(

ui=fluidPage(
  
  # Application title
  titlePanel("Linear regression of mpg by selected variable"),
  
  # Sidebar with a slider input 
  sidebarLayout(
    sidebarPanel(
      h4("Select a variable and submit to calculate coefficients"),
      selectInput("variable","Variable:", c("cyl","qsec","am")),
      submitButton("Submit")
    ),
    
    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("plot1")
    )
  )
),

server=function(input, output) {
  data(mtcars)
  model<- reactive({
    varInput<-input$variable
    colnum<-match(varInput,names(mtcars))
    df<-data.frame(mpg=mtcars$mpg,mtcars[,colnum])
    colnames(df)[2]<-varInput
    fit<-lm(mpg~.,data=df)
  })   

  output$plot1<-renderPlot({
    varInput<-input$variable
    colnum<-match(varInput,names(mtcars))
    df<-data.frame(mpg=mtcars$mpg,mtcars[,colnum])
    colnames(df)[2]<-varInput
    plot(df[,2],df$mpg,xlab=colnames(df)[2],
         ylab="mpg")
    abline(model(),col="red",lwd=2)
  })
  
},
)
```

## End

Thank you for your attention.

Feel free to visit the Github repo with all code detail at https://github.com/valors/shiny

